%Statement of the problem?
%Why the problem appears?
%how solve the problem (design and methods)
%new contriubution



%################################################################
%why you did the work and what you were trying to achieve;

%What methods you used and what results you obtained?

%Conclusions

\vspace*{-0.5cm}

In recent years, the \glspl{mpsoc} complexity has been growing exponentially nevertheless, the performance of simulation tools is not 
following this growth, mainly because of their sequential simulation type. Therefore, simulation time increases each time a new \gls{mpsoc} 
is developed. Concerning this problem, the \gls{ice} \gls{rwth} Aachen team developed a parallel version of the atomic mode of Gem5, par-gem5. 
It is based on a synchronous \gls{pdes} which allows each simulation thread to run independently from the rest of the system for a time 
$t_{\Delta q}$ - the so-called quantum. Although this is a huge improvement, it carries a challenge in the quantum definition. 
Additionally, as systems become more complex, the necessity of iteration between distinct simulators grows because different aspects must be 
taken into account. 

This dissertation aims to solve two problems. The first one is the optimal quantum finding, which can lead to the best trade-off between 
accuracy and performance. Nowadays, par-gem5 is bound to a static quantum which cannot be changed during run-time however, an adaptive 
version can overcome this limitation. It was conceptualized and developed a flexible algorithm that can operate independently of 
the used benchmark and system. The second problem is the iteration between Gem5 and other simulators. At its current state, it lacks in this topic since few available 
frameworks can work with this tool. Thereby, it was proposed a co-simulation environment that can integrate any 
simulator. Further, it was chosen a study case in order to validate the developed framework. 

In the end, the dynamic version of the quantum choice brings greater benefits when compared with the present solution. It was possible to achieve, 
on average, a performance gain of almost 10\%, only sacrificing 0.5\% of accuracy. Nevertheless, when a-priori information about the 
test is given, the tradeoff can be improved with the static approach thus, it should not be fully discarded. 
If perfect accuracy is a requirement, the sequential version must be used, since the usage of both methods implies a loss in accuracy. 
Moreover, the proposed framework provided a new work environment. It maintained data integrity, data exchange, and synchronization 
between the tools during all the simulations. With this work, a new contribution to this subject was provided.

\paragraph{}\textbf{Keywords:} Parallel Discrete Event Simulation, Gem5, Full-System Simulation, Quantum, Co-Simulation
